---
title: "Incongruence"
format: html
editor: visual
execute: 
  echo: false
  warning: false
---

```{r}
source("../scripts/generate_table.R")
generate_table("Incongruence")
```

## Hypothesis

**Research Questions**

The study investigates how high levels of incongruence in basic psychological needs manifest through micro-PK effects, focusing on attachment, self-esteem protection, and orientation/control needs. These needs, based on [@grawe1998psychologische] model, can be satisfied through approach or avoidance goals. The need for pleasure maximization and distress avoidance was excluded due to operationalization challenges. The study hypothesizes that unconscious motivational patterns influence the outcomes of a true random number generator (tRNG), rather than conscious attempts to manipulate it.

**Hypotheses**

A)  High-Incongruence of Needs and Micro-PK

<!-- -->

1.  *Attachment*: Participants with high incongruence in the need for attachment are expected to show fewer attachment-related target stimuli than chance suggests.

2.  *Self-Esteem*: High-incongruence participants for self-esteem protection will show more self-esteem-related target stimuli than chance.

3.  *Control*: Those with high incongruence in orientation and control will experience more non-control trials than chance.

<!-- -->

B)  Low-Incongruence of Needs and Micro-PK

<!-- -->

1.  *General*: Low-incongruence participants are expected to show no deviation from chance.

2.  *Attachment*: Since attachment is growth-oriented, low-incongruence participants might show a less strong deviation in the same direction as high-incongruence participants.

3.  *Self-Esteem and Control*: As these needs are deficiency-oriented, low-incongruence participants might show no deviation or a less strong deviation in the opposite direction compared to high-incongruence participants.

<!-- -->

## Participants

```{r}
library(tidyverse)
library(knitr)

df <- study9_incongruence

# Data
total_participants <- nrow(df)
mean_age <- mean(df$Alter, na.rm=T)
sd_age <- sd(df$Alter, na.rm=T)
female_count <- sum(df$Geschlecht == 1, na.rm=T)
male_count <- sum(df$Geschlecht == 2, na.rm=T)

# Create the table
table_data <- data.frame(
  Characteristic = c("N", "Female", "Male", "Mean Age", "SD Age"),
  Count_Statistics = c(
    total_participants,
    female_count,
    male_count,
    paste0(round(mean_age, 2), " years"),
    paste0(round(sd_age, 2), " years")
    )
)

# Print the table using kable
kable(table_data, format = "html", col.names = c("Characteristic", "Count/Statistic")) %>%
  kableExtra::kable_styling(full_width = FALSE)

```

## Materials

This was an online study.

**Study design**

The study was conducted online, using a between-subjects design. Participants were divided into two groups (low-incongruence vs. high-incongruence) based on their scores on the "Inkongruenzfragebogen (INK)" [@grosse2004inkongruenzfragebogen]. The division point was the standardized average value for healthy individuals as specified in the manual.

**Measured variables**

1)  *Attachment*: Target stimuli consisted of 20 pictures of happy couples, sourced from Shutterstock, aimed at addressing the need for attachment. Neutral stimuli, sourced from the OASIS picture set [@kurdi2016], included 20 pictures of everyday objects rated low on arousal and neutral in valence. The outcome variable for attachment was the number of displayed target stimuli.

2)  *Self-esteem*: The target stimuli included negatively perceived adjectives that challenge self-esteem (e.g., "ugly," "worthless," "stupid"), corresponding to dimensions in the "Feelings of Inadequacy Scale" [@1960-07155-005]. Neutral stimuli included adjectives describing geometric figures and surface textures (e.g., "five-cornered," "dotted"). The outcome variable for self-esteem was the number of displayed target stimuli.

3)  *Control*: To test the need for orientation and control, participants were shown unpleasant pictures from the International Affective Pictures System (IAPS) [@lang1999international], which have a negative valence and high arousal. In control trials, participants could end the display by pressing a button, whereas in non-control trials, the display lasted 2500 ms regardless of button press. 75% of the trials allowed for control over the presentation time. The outcome variable for control was the number of non-control trials.

## Procedure

Participants were tested in a lab with ten identical computers, each separated by dividers. The entire experiment lasted around 30 minutes. An experimenter explained the procedure using a standardized script and answered any participant questions. Once ready, participants began by completing the INK questionnaire and then proceeded to the image display by pressing any button.

The experiment consisted of three micro-PK tasks performed in the following order: "attachment," "self-esteem protection," and "loss of control." Each task involved three series of ten trials, totaling 30 trials. Participants viewed a fixation cue for 700 ms, then a stimulus (pictures for 400 ms; words for 800 ms), followed by a black screen for 400 ms.

For each trial, a quantum random number generator (QRNG) determined whether the stimulus would be need-related or neutral, and BitBabbler’s randomization function selected the specific stimulus from the chosen set. The QRNG’s randomization ensured that the selected stimulus was either from a need-related set or a neutral set.

After the third task, participants completed a post-task questionnaire. They rated the unpleasantness of the disgusting pictures on a scale from 1 (very unpleasant) to 5 (not at all unpleasant) and shared their assumptions about the study's purpose.

::: {.callout-tip title="Data" collapse="false"}
-   [Download Data](../data/incongruence/incongruence.csv)
-   [Download Data "High"](../data/incongruence/incongruence_high.csv)
-   [Download Data "Low"](../data/incongruence/incongruence_low.csv)
:::

::: {.callout-note title="Resources" collapse="false"}
-   [Publication](https://www.parapsychologypress.org/jparticle/jp-84-2-227-253) [@jakob2020]
-   [Preregistration](https://osf.io/xm4wf)
-   [OSF Project](https://osf.io/gnryu/)
-   [Experimental Program](../data/incongruence/ink.html)
-   [Questionnaire](../data/incongruence/variables_bink_2017-05-23_15-57.csv)
-   [Stimuli](../data/incongruence/INK.zip)
:::
