---
title: "Meditation"
format: html
editor: visual
execute: 
  echo: false
  warning: false
---

```{r}
library(tidyverse)
library(knitr)

load("../study_objects.RData")
```

## Hypothesis

Participants were asked to 2 runs of stimuli perception. Before the first run, a prerecorded relaxation exercise was played back. For the second run, they were asked to put themselves in a meditative state. Stimuli consisted of a combination of either positive images and sounds or negative images and sounds. We hypothesized more positive stimuli ("hits") in the second run after the meditation.

## Participants

```{r}
# library(tidyverse)
# library(knitr)
# 
# df <- study4_meditation
# 
# # Data
# total_participants <- nrow(df)
# mean_age <- mean(df$DE02_01, na.rm=T)
# sd_age <- sd(df$DE02_01, na.rm=T)
# female_count <- sum(df$DE01 == 1, na.rm=T)
# male_count <- sum(df$DE01 == 2, na.rm=T)
# other_count <- sum(df$DE01 == 3, na.rm=T)
# 
# # Create the table
# table_data <- data.frame(
#   Characteristic = c("N", "Female", "Male", "Other", "Mean Age", "SD Age"),
#   Count_Statistics = c(
#     total_participants, 
#     female_count, 
#     male_count,
#     other_count,
#     paste0(round(mean_age, 2), " years"), 
#     paste0(round(sd_age, 2), " years")
#     )
# )
# 
# # Print the table using kable
# kable(table_data, format = "html", col.names = c("Characteristic", "Count/Statistic")) %>%
#   kableExtra::kable_styling(full_width = FALSE)
print("Demographic Data Not Available")

```

## Materials

Picture stimuli comprised 100 positive and 100 negative images further described in study 12. Audio stimuli comprised two consonant chords and two dissonant chords. The relaxation exercise consisted of a 2-minute prerecorded audio file asking participants to focus on their breathing and become peaceful and relaxed.

## Procedures

Participants were tested online. After welcoming them audio playback was tested to ensure the correct playback of sound stimuli. A prerecorded relaxation audio file was read to them (2 mins). They were then asked to attentively perceive a set of 100 trial presentations consisting of images and sounds. After this set, they were asked to put themselves in a meditative state. They could choose the meditative practice and duration freely, but it was noted that most chose a duration between 10 and 30 minutes. After the meditation they were again presented with 100 trials consisting of either a randomly chosen positive picture and sound or negative picture and sound. They were then thanked and asked to fill out some questions.

::: {.callout-tip title="Data" collapse="true"}
[Download Data](../data/meditation.csv)
:::

::: {.callout-note title="Resources" collapse="true"}
-   [Experimental Program](https://osf.io/hjxad)
-   [Questionnaire Structure](https://osf.io/4asug)
-   [Relaxation Audio](https://osf.io/9gnds)
-   [Relaxation Audio English](https://osf.io/pbzrv)
:::
