---
title: "Meditation"
format: html
execute: 
  echo: false
  warning: false
---

```{r}
source("../scripts/generate_table.R")
generate_table("Meditation")
```

## Hypothesis

Participants were asked to 2 runs of stimuli perception. Before the first run, a prerecorded relaxation exercise was played back. For the second run, they were asked to put themselves in a meditative state. Stimuli consisted of a combination of either positive images and sounds or negative images and sounds. We hypothesized more positive stimuli ("hits") in the second run after the meditation.

## Participants

```{r}

print("Demographic Data Not Available")

```

## Materials

Picture stimuli comprised 100 positive and 100 negative images further described in study 12. Audio stimuli comprised two consonant chords and two dissonant chords. The relaxation exercise consisted of a 2-minute prerecorded audio file asking participants to focus on their breathing and become peaceful and relaxed.

## Procedure

Participants were tested online. After welcoming them audio playback was tested to ensure the correct playback of sound stimuli. A prerecorded relaxation audio file was read to them (2 mins). They were then asked to attentively perceive a set of 100 trial presentations consisting of images and sounds. After this set, they were asked to put themselves in a meditative state. They could choose the meditative practice and duration freely, but it was noted that most chose a duration between 10 and 30 minutes. After the meditation they were again presented with 100 trials consisting of either a randomly chosen positive picture and sound or negative picture and sound. They were then thanked and asked to fill out some questions.

## Results of Universal Micro-PK Hypothesis

::: {.panel-tabset}

## Bayes Factor
```{r}
generate_bfplot(list(
  T1 = study4_meditation.t1$BF,
  T2 = study4_meditation.t2$BF
))
```

## Random Walk
```{r}
generate_rwplot(list(
  T1 = study4_meditation.t1$sums,
  T2 = study4_meditation.t2$sums
), 100)

```

## Change of Evidence
### T1
```{r}
generate_coeplot(study4_meditation.t1$BF)
```
### T2
```{r}
generate_coeplot(study4_meditation.t2$BF)
```
:::

::: {.callout-tip title="Data" collapse="false"}
-   [Download Data](../data/meditation/meditation.csv)
:::

::: {.callout-note title="Resources" collapse="false"}
-   [Experimental Program](https://github.com/mrzdcmps/labreport/blob/main/data/meditation/nmedi_org.html)
-   [Questionnaire Structure](../data/meditation/survey.nmedi-e.2017-12-16.xml)
-   [Relaxation Audio](../data/meditation/entspannung.mp3)
-   [Relaxation Audio English](../data/meditation/entspannung_e.mp3)
:::
