---
title: "Prayer"
format: html
execute: 
  echo: false
  warning: false
---

```{r}
source("../scripts/generate_table.R")
generate_table("Prayer")
```

## Hypothesis

Participants were asked to pray to enter a state of devotion. Subsequently they were presented a combination of either positive images and sounds or negative images and sounds. We hypothesized more positive stimuli ("hits").

## Participants

```{r}
generate_demographics_table(
  data = study2_prayer,
  age_col = "DE02_01",
  gender_col = "DE01",
  male_value = "2",
  female_value = "1",
  other_value = "3"
)
```

## Materials

Picture stimuli comprised 100 positive and 100 negative images further described in study 12. Audio stimuli comprised two consonant chords and two dissonant chords.

## Procedure

Participants were tested online. After welcoming them audio playback was tested to ensure the correct playback of sound stimuli. They were then asked to to enter a devotional state through prayer. They could choose freely how long to pray, but it was noted that most chose a duration between 10 and 30 minutes. After the prayer they were presented with 100 trials consisting of either a randomly chosen positive picture and sound or negative picture and sound. They were then thanked and asked to fill out some questions.

## Results of Universal Micro-PK Hypothesis

::: {.panel-tabset}
## Bayes Factor
```{r}
generate_bfplot(study2_prayer$BF)
```

## Random Walk
```{r}
generate_rwplot(study2_prayer$Pos, 100)
```

## Change of Evidence
```{r}
generate_coeplot(study2_prayer$BF)
```
:::

::: {.callout-tip title="Data" collapse="false"}
-   [Download Data](../data/prayer/prayer.csv)
:::

::: {.callout-note title="Resources" collapse="false"}
-   [Experimental Program](https://github.com/mrzdcmps/labreport/blob/main/data/prayer/nmedi_b.html)
-   [Questionnaire](../data/prayer/questionnaire.csv)
:::
