---
title: "Prayer"
format: html
editor: visual
execute: 
  echo: false
  warning: false
---

```{r}
library(tidyverse)
library(knitr)

load("../study_objects.RData")
```

## Hypothesis

Participants were asked to pray to enter a state of devotion. Subsequently they were presented a combination of either positive images and sounds or negative images and sounds. We hypothesized more positive stimuli ("hits").

## Participants

```{r}
library(tidyverse)
library(knitr)

df <- study2_prayer

# Data
total_participants <- nrow(df)
mean_age <- mean(df$DE02_01, na.rm=T)
sd_age <- sd(df$DE02_01, na.rm=T)
female_count <- sum(df$DE01 == 1, na.rm=T)
male_count <- sum(df$DE01 == 2, na.rm=T)
other_count <- sum(df$DE01 == 3, na.rm=T)

# Create the table
table_data <- data.frame(
  Characteristic = c("N", "Female", "Male", "Other", "Mean Age", "SD Age"),
  Count_Statistics = c(
    total_participants, 
    female_count, 
    male_count,
    other_count,
    paste0(round(mean_age, 2), " years"), 
    paste0(round(sd_age, 2), " years")
    )
)

# Print the table using kable
kable(table_data, format = "html", col.names = c("Characteristic", "Count/Statistic")) %>%
  kableExtra::kable_styling(full_width = FALSE)

```

## Materials

Picture stimuli comprised 100 positive and 100 negative images further described in study 12. Audio stimuli comprised two consonant chords and two dissonant chords.

## Procedures

Participants were tested online. After welcoming them audio playback was tested to ensure the correct playback of sound stimuli. They were then asked to to enter a devotional state through prayer. They could choose freely how long to pray, but it was noted that most chose a duration between 10 and 30 minutes. After the prayer they were presented with 100 trials consisting of either a randomly chosen positive picture and sound or negative picture and sound. They were then thanked and asked to fill out some questions.

::: {.callout-tip title="Data" collapse="true"}
[Download Data](../data/prayer.csv)
:::

::: {.callout-note title="Resources" collapse="true"}
-   [Questionnaire](https://osf.io/rfzv8)
-   [Experimental Program](https://osf.io/y6f57)
:::
