---
title: "Priming 2"
format: html
execute: 
  echo: false
  warning: false
---

```{r}
source("../scripts/generate_table.R")
generate_table("Priming 2")
```

## Hypothesis

This study was a direct replication of [Priming 1](priming1.html). All predictions were identical to those in the first study.

## Participants

```{r}
generate_demographics_table(
  data = study13_priming.2,
  age_col = "s2",
  gender_col = "gender_image",
  male_value = "1",
  female_value = "2"
)
```

## Materials and Procedure

All materials and procedures were identical to those in [Priming 1](priming1.html).

## Sample Size and Data Analysis

Participant recruitment and data collection for the study were conducted by Norstat, following the same protocol as Study 1. Initially, data collection was planned to stop when the sequential Bayes Factor (BF) reached the predefined threshold, which occurred at n = 937. However, due to concerns about the small predicted effect size and potential lack of statistical power, the researchers decided to continue collecting data. They closely monitored the BF and eventually stopped recruitment when the sample size reached N = 2,063. Demographic data were available for 2,021 participants.

## Results of Universal Micro-PK Hypothesis

::: {.panel-tabset}

## Bayes Factor
```{r}
generate_bfplot(list(
  exp = study13_priming.2$expbf,
  con = study13_priming.2$conbf
))
```

## Random Walk
```{r}
generate_rwplot(list(
  exp = study13_priming.2$sumsexp,
  con = study13_priming.2$sumscon
), 20)

```

## Change of Evidence
### Exp
```{r}
generate_coeplot(study13_priming.2$expbf)
```
### Con
```{r}
generate_coeplot(study13_priming.2$conbf)
```
:::

::: {.callout-tip title="Data" collapse="false"}
-   [Download Data](../data/priming/priming2.csv)
:::

::: {.callout-note title="Resources" collapse="false"}
-   [Publication](https://journals.lub.lu.se/jaex/article/view/23205) [@dechamps2021]
-   [Preregistration](https://osf.io/83efr)
-   [OSF Project](https://osf.io/hgxt3)
-   [Analyses](https://osf.io/hgxt3/files/osfstorage)
-   [Experimental Program](https://github.com/mrzdcmps/labreport/blob/main/data/priming/n-prime.html)
-   [Stimuli](../data/priming/NPrime.zip)
:::
