---
title: "Smokers 3"
format: html
editor: visual
execute: 
  echo: false
  warning: false
---

```{r}
source("../scripts/generate_table.R")
generate_table("Smokers 3")
```

## Hypothesis

In this study, we used cigarette addiction as unconscious drive (see [Smokers 1](smokers1.html) and [Smokers 2](smokers2.html)). We hypothesized that smoking participants would influence the outcome of a qRNG in such a way that the effect follows a specific pattern derived from post-hoc analyses of the previous studies.

## Participants

```{r}
library(tidyverse)
library(knitr)

df <- subset(study10_smokers, Study == 3)

# Data
total_participants <- nrow(df)
mean_age <- mean(df$Age, na.rm=T)
sd_age <- sd(df$Age, na.rm=T)
female_count <- sum(df$Sex == 1, na.rm=T)
male_count <- sum(df$Sex == 2, na.rm=T)

# Create the table
table_data <- data.frame(
  Characteristic = c("N", "Female", "Male", "Mean Age", "SD Age"),
  Count_Statistics = c(
    total_participants,
    female_count,
    male_count,
    paste0(round(mean_age, 2), " years"),
    paste0(round(sd_age, 2), " years")
    )
)

# Print the table using kable
kable(table_data, format = "html", col.names = c("Characteristic", "Count/Statistic")) %>%
  kableExtra::kable_styling(full_width = FALSE)

```

## Materials

All materials and procedural decisions were identical to those of Studies [1](smokers1.html) and [2](smokers2.html).

## Sample Size and Data Analyses

Participants were added until a total of 500 smokers had been reached, including all participants from Studies 1 and 2.

We hypothesized a non-linear effect development resulting in the cumulative z-score of all studies following a fitted dampened harmonic oscillation. To test this hypothesis, we compared the actual cumulative z-score to that of 10,000 simulations and predicted a closer match than 5% of simulations for the following test statistics:

1.  The area between the experimental data curve and the prediction.
2.  The Euclidian distance of the local maximum compared with that of the prediction.
3.  The Euclidian distance of the end point compared with that of the end point of the prediction.

::: {.callout-tip title="Data" collapse="false"}
-   [Download Data](../data/smokers/smokers3.csv)
:::

::: {.callout-note title="Resources" collapse="false"}
-   [Publication](https://journalofscientificexploration.org/index.php/jse/article/view/1513) [@dechamps2019]
-   [Preregistration](https://osf.io/r6z8y)
-   [OSF Project](https://osf.io/wk9es)
:::
