---
title: "Willpower"
format: html
execute: 
  echo: false
  warning: false
---

```{r}
source("../scripts/generate_table.R")
generate_table("Willpower ")
```

## Hypothesis

This experiment was developed by students in an empirical course. We aimed to explore the complementary relationship between willpower and objectification, with a focus on how affect might influence this dynamic. We hypothesized that reducing objectivity in measurement, specifically by partially deleting objective data, could enhance willpower, operationalized as vitality, by creating a more "sobjective" (subjective-objective) experimental environment. This approach was inspired by the Model of Pragmatic Information, which suggests that maximum information transfer occurs when novelty and confirmation are balanced, a state achievable by moderating objectivity.

Our first hypothesis was that participants in the "delete condition" (where objective data was erased) would exhibit higher vitality compared to those in the "save condition" (where data was retained), as the reduced objectivity might foster a more favorable unconscious state for micro-psychokinesis (micro-PK) effects. Additionally, we investigated the role of affect, proposing that positive affect would correlate with both the number of positive images received from a quantum random number generator (qRNG) (Hypothesis 2) and the number of positive images subjectively remembered by participants (Hypothesis 3). These hypotheses were based on the idea that emotional states could influence the manifestation of micro-PK effects, either objectively or subjectively.

We also included supplementary hypotheses to further examine potential micro-PK effects. Hypothesis 4 predicted that participants in the delete condition would remember more positive images, indicating a subjective micro-PK effect, while Hypothesis 5 anticipated that the objectively recorded number of positive images would exceed chance levels, suggesting an objective micro-PK effect. Finally, we explored the relationships between vitality and two additional variables: implicit theory of willpower (Hypothesis 6) and ego depletion (Hypothesis 7). These hypotheses were designed to assess whether these factors could serve as proxies or complementary measures for vitality in future research.

## Participants

```{r}
generate_demographics_table(
  data = study25_willpower.save,
  age_col = "age",
  gender_col = "gender",
  male_value = "männlich",
  female_value = "weiblich"
)
```

## Materials

A qRNG was used to select visual stimuli from a pool of 115 images, consisting of 100 positive and 15 neutral pictures sourced from the *Open Affective Standardized Image Set (OASIS)* database. The positive images were chosen for their emotional salience, while the neutral ones were selected for low arousal and medium valence.  

To measure psychological variables, we used several validated questionnaires:  

- *Vitality* was assessed using a modified German Subjective Vitality Scale (SVS-GM), with three items rated on a 10-point scale.  
- *Implicit theory of willpower* was measured via a 6-item scale (Job et al., 2010), assessing beliefs about willpower as either limited or unlimited.  
- *Ego depletion* (current self-control capacity) was evaluated using the SMS-5 questionnaire (Lindner et al., 2019), a 5-item scale with a 7-point response range.  
- *Affect* was captured qualitatively through a free-text field where participants described their emotional state; responses were later coded on a 5-point scale (-2 to +2).  
The study also included a brief *autonomy assessment* (Janke & Glöckner-Rist, 2012), though this variable was not central to our hypotheses. The experiment followed a between-subjects design with two conditions: one where qRNG-generated image data was deleted ("delete condition") and another where it was saved ("save condition"). All materials were presented in German or English, depending on participant preference.  

## Procedure

The experiment began with an introductory screen explaining the task: participants were told they would view a series of images and should use their willpower to try to see as many positive images as possible. After providing informed consent, they proceeded to describe their current emotional state in a free-text field, which was later coded for affect.  

Next, participants were shown examples of positive and neutral images to familiarize them with the stimuli. They then entered the main experimental phase, consisting of 20 trials. Each trial followed the same sequence:  

1. A 2-second display of the phrase *"Believe in your willpower!"* to prime intentionality.
2. A 500-millisecond black screen as an interstimulus interval.  
3. A 2-second display of an image (positive or neutral) selected by the quantum random number generator (qRNG).  
4. A 1-second black screen before the next trial.  

After completing the trials, participants answered questionnaires assessing ego depletion, vitality, and implicit theory of willpower, followed by an estimate of how many positive images they believed they had seen. Finally, they provided demographic information (age, gender) before concluding the study.  

The experiment employed a *between-subjects design*:  
- In the "delete condition" (N=248), the qRNG’s objective image data was erased after temporary storage.  
- In the "save condition" (N=257), the data was permanently retained.  

## Sample Size and Data Analysis

Sample size consisted of participants collected for an empirical course and a later continuation of a single student. 

For confirmatory analysis, we employed Bayesian statistical methods to assess evidence for our hypotheses while accounting for the small expected effect sizes typical in micro-PK research. Key analyses included:  

- Bayesian independent-samples *t*-tests (one-tailed, Cauchy prior *r* = 0.1) to compare vitality between the delete and save conditions (Hypothesis 1) and to evaluate subjective recall of positive images (Hypothesis 4).  
- Bayesian one-sample *t*-tests to check whether the number of objectively received positive images exceeded chance (Hypothesis 5).  
- Bayesian Pearson correlations (stretched beta prior width = 0.1) to examine relationships between affect and objective/subjective image counts (Hypotheses 2 & 3) and between vitality, implicit theory of willpower, and ego depletion (Hypotheses 6 & 7).  

We also conducted exploratory analyses, including subgroup comparisons by gender and age, using the same Bayesian framework. Classical frequentist *t*-tests (α = .05) supplemented these analyses to estimate effect sizes (Cohen’s *d*).  

A Bayesian ANCOVA further explored how ego depletion and implicit willpower theories influenced vitality across conditions. All analyses were performed in JASP (v0.18.3), with Bayes Factors (BF₁₀) interpreted as follows:  
- *BF₁₀ > 10* → Strong evidence for the alternative hypothesis (H₁).  
- *BF₁₀ < 1/10* → Strong evidence for the null (H₀).  
- *Values near 1* → Inconclusive results.  

Despite the robust design, most hypotheses yielded anecdotal-to-moderate evidence for H₀ suggesting no clear effects—though small trends in predicted directions left room for further investigation with larger samples.

## Lab Report Data
For the lab report, only objective qRNG of the save-condition and no subjective estimates are included.


::: {.callout-tip title="Data" collapse="false"}
-   [Download All Data](../data/willpower/willpower.csv)
-   [Download Data of Save Condition](../data/willpower/willpower-save.csv)
:::

::: {.callout-note title="Resources" collapse="false"}
-   [Student Report](../data/stories/willpower-report.pdf)
-   [Experimental Program](https://github.com/mrzdcmps/labreport/blob/main/data/willpower/wille.html)
:::
