---
title: "CoE Meta-Analysis"
format: 
  html:
    page-layout: full
editor: visual
page-navigation: true
---

Last update: 04 May 2020

## Meta-Analysis of Change of Evidence Measures

In these meta-analyses, we will analyze the overall significance of the change of evidence-measures in all experimental and control studies. Since we don't have effect sizes for these measures, we will combine the empirical p-values of the studies, this means, we will analyze the amount of simulations that show an equal or higher value in the maxbf, energybf, and frequency tests than the empirical BF.

The resulting p-values will be analyzed using the inverse chi-square method, which converts each p-value into a chi-square statistic and then sums them up. The method allows for the incorporation of different degrees of freedom, making it particularly useful when the p-values come from tests with varying sample sizes.

::: panel-tabset
## Experimental Studies

In this analysis all Micro-Pk studies of the LMU Micro-Pk Lab are included that hypothesize the **presence** of an effect. In studies comparing experimental to control conditions, only the experimental conditions are included.

```{r}
coe <- readRDS("data/coe.rds")

# Select studies / conditions
data <- subset(coe, coe$Experimental == TRUE)

knitr::kable(data)

library(metap)
istwo <- ifelse(data$Direction == "different", TRUE, FALSE) # two-tailed test
df <- data$N-1 # degrees of freedom
```

### Max BF

```{r}
pvals <- two2one(data$`MaxBF p`, istwo)

res <- invchisq(pvals, k=df)
print(res)
plot(res)
```
### BF Energy

```{r}
pvals <- two2one(data$`Energy p`, istwo)

res <- invchisq(pvals, k=df)
print(res)
plot(res)
```

### FFT Amplitude Sum

```{r}
pvals <- two2one(data$`FFT p`, istwo)

res <- invchisq(pvals, k=df)
print(res)
plot(res)
```

### Robustness to Sample Sizes

In comparison to the inverse chi-square method, which weights each p-value by its degree of freedom and therefor its sample size, Fisher's method combines p-values by taking the sum of their logarithms and then comparing them to a chi-square distribution. This method is less sensitive to sample sizes and can be used as a robustness check countering arguments of selectively continuing data collection of studies with a noticeable BF.

```{r}
#Max BF
pvals <- two2one(data$`MaxBF p`, istwo)
sumlog(pvals)

#Energy BF
pvals <- two2one(data$`Energy p`, istwo)
sumlog(pvals)

#FFT Amplitude Sum
pvals <- two2one(data$`FFT p`, istwo)
sumlog(pvals)
```


## Control Studies

In this analysis all Micro-Pk studies of the LMU Micro-Pk Lab are included that hypothesize the **absence** of an effect. In studies comparing experimental to control conditions, only the control conditions are included.

```{r}
# Select studies / conditions
data <- subset(coe, coe$Experimental == FALSE)
knitr::kable(data)

library(metap)
istwo <- ifelse(data$Direction == "different", TRUE, FALSE) # two-tailed test
df <- data$N-1 # degrees of freedom
```

### Max BF

```{r}
pvals <- two2one(data$`MaxBF p`, istwo)
res <- invchisq(pvals, k=df)
print(res)
plot(res)
```
### BF Energy

```{r}
pvals <- two2one(data$`Energy p`, istwo)
res <- invchisq(pvals, k=df)
print(res)
plot(res)
```

### FFT Amplitude Sum

```{r}
pvals <- two2one(data$`FFT p`, istwo)
res <- invchisq(pvals, k=df)
print(res)
plot(res)
```

### Robustness to Sample Sizes

```{r}
#Max BF
pvals <- two2one(data$`MaxBF p`, istwo)
sumlog(pvals)

#Energy BF
pvals <- two2one(data$`Energy p`, istwo)
sumlog(pvals)

#FFT Amplitude Sum
pvals <- two2one(data$`FFT p`, istwo)
sumlog(pvals)
```
:::
