---
title: "Experiments"
format: 
  html:
    page-layout: full
    css: "//netdna.bootstrapcdn.com/bootstrap/3.0.0/css/bootstrap-glyphicons.css"
toc: true
toc-depth: 3
editor: visual
execute: 
  echo: false
  warning: false
bibliography: references.bib
csl: apa.csl
---

Last update: 04 May 2020

## Overview

```{r}
st <- readRDS("overview.rds")

library(formattable)
formattable(format(st, digits=2, nsmall = 2, scientific=F),
            align = c("l",rep("c", NCOL(st) - 1)),
            list(`Hits (%)` = color_tile("coral2","cornflowerblue"),
                 `Experimental condition` = formatter("span", 
                                   x ~ icontext(ifelse(x == F, "remove", "ok")), 
                                   style = x ~ style(color = ifelse(x == F, "red", "green"))),
                 `p` = formatter("span",
                                     style = x ~ style("font-weight" = ifelse(x <= 0.05, "bold", NA))),
                 `Labstudy` = formatter("span", 
                                   x ~ icontext(ifelse(x == F, "globe", "home")), 
                                   style = x ~ style(color = ifelse(x == F, "royalblue", "darkblue")))))

```

## Description of Experiments

### General Information

#### Generation of Randomness

When not specified otherwise, we used a quantum-based random number generator (qRNG) *Quantis* by idquantique to generate true randomness and coupled the outcome of these random events to the display of relevant stimulus material. A micro-Pk effect should result in a (temporary; see [*change of evidence*](changeofevidence.html)) biasing of the qRNG outcome corresponding to the presentation of more or less of the relevant stimuli.

#### Online Studies

If an experiment is classified as an online study, it was set up with the software jsPsych [@deleeuw2023] and running on a dedicated web server in the departments IT infrastructure. A qRNG is directly connected to the web server via USB and provides random events without a buffer.

```{r}
# load study data
load("study_objects.RData")
```

### Loving Kindness

#### Hypothesis

Participants underwent a pre-recorded "loving kindness"-meditation. At the end of the hypnosis they were asked to listen to sounds that were either classified *neutral* (white noise) or *meditation-related* (singing bowl; mantra). We hypothesized an increase of meditation-related sounds ("hits").

#### Participants

```{r}
library(tidyverse)
library(knitr)

df <- study1_lovingkind

# Data
total_participants <- nrow(df)
mean_age <- mean(df$DE02_01)
sd_age <- sd(df$DE02_01)
female_count <- sum(df$DE01 == 1)
male_count <- sum(df$DE01 == 2)

# Create the table
table_data <- data.frame(
  Characteristic = c("N", "Female", "Male", "Mean Age", "SD Age"),
  Count_Statistics = c(
    total_participants, 
    female_count, 
    male_count,
    paste0(round(mean_age, 2), " years"), 
    paste0(round(sd_age, 2), " years")
  )
)

# Print the table using kable
kable(table_data, format = "html", col.names = c("Characteristic", "Count/Statistic")) %>%
  kableExtra::kable_styling(full_width = FALSE)

```

#### Materials

We used a guided meditation by Inga Jagadamba Stendel as guided loving kindness meditation. Target sounds consisted of singing bowl sounds in f-key and a chanted "Yam"-sound. In spiritual acoustics the f-key corresponds with the frequency of the heart chakra, which according to yogic teaching is responsible for the experience and processing of love and kindness and related emotions. The chanted "Yam"-sound is one of the seven Bija-mantras and is attributed to the heart-chakra as well (Bodian, 2007).

#### Procedures

Participants were tested in the laboratory in a quiet and distraction-free environment. The experimenters introduced themselves and read a standardized instruction. Participants were asked to sit comfortably and listen to a guided loving-kindness meditation (ca. 13 mins) which then transition to the experimental part and the playback of the sounds. Participants listened to a total of 100 sounds before transitioning back to the ending of the guided meditation. All sounds were5 seconds long and are edited to fade out.

Additional questions were asked concerning native language, experience with meditation, subjective effect of the meditation, experienced emotions during meditation and sound display, and ratings of the stimuli.

::: {.callout-tip title="Data" collapse="true"}
```{r}
#write_excel_csv(study1_lovingkind, "study1.csv")
```
[Download .csv](data/lovingkind.csv)
:::

::: {.callout-note title="Resources" collapse="true"}
-   [Preregistration](https://osf.io/g92ts)
-   [Questionnaire](https://osf.io/qzj9m)
-   [Experimental Program](https://osf.io/xebd5)
:::

### Prayer

#### Hypothesis

Participants were asked to pray to enter a state of devotion. Subsequently they were presented a combination of either positive images and sounds or negative images and sounds. We hypothesized more positive stimuli ("hits").

#### Participants

```{r}
library(tidyverse)
library(gt)

df <- study2_prayer

# Data
total_participants <- nrow(df)
mean_age <- mean(df$DE02_01, na.rm=T)
sd_age <- sd(df$DE02_01, na.rm=T)
female_count <- sum(df$DE01 == 1, na.rm=T)
male_count <- sum(df$DE01 == 2, na.rm=T)
other_count <- sum(df$DE01 == 3, na.rm=T)

# Create the table
table_data <- data.frame(
  Characteristic = c("N", "Female", "Male", "Other", "Mean Age", "SD Age"),
  Count_Statistics = c(
    total_participants, 
    female_count, 
    male_count,
    other_count,
    paste0(round(mean_age, 2), " years"), 
    paste0(round(sd_age, 2), " years")
    )
)

# Print the table using kable
kable(table_data, format = "html", col.names = c("Characteristic", "Count/Statistic")) %>%
  kableExtra::kable_styling(full_width = FALSE)

```

#### Materials

Picture stimuli comprised 100 positive and 100 negative images further described in study 12. Audio stimuli comprised two consonant chords and two dissonant chords.

#### Procedures

Participants were tested online. After welcoming them audio playback was tested to ensure the correct playback of sound stimuli. They were then asked to to enter a devotional state through prayer. They could choose freely how long to pray, but it was noted that most chose a duration between 10 and 30 minutes. After the prayer they were presented with 100 trials consisting of either a randomly chosen positive picture and sound or negative picture and sound. They were then thanked and asked to fill out some questions.

::: {.callout-tip title="Data" collapse="true"}
[Download .csv](data/prayer.csv)
:::

::: {.callout-note title="Resources" collapse="true"}
-   [Questionnaire](https://osf.io/rfzv8)
-   [Experimental Program](https://osf.io/y6f57)
:::

### Monks

#### Hypothesis

In this experiment we tested experienced meditators and monks and explored their influence on the outcome of an qRNG which corresponded to neutral and negative images. Every person participated in two runs. While they did not know about the goal of study for the first run, experimenters explained to them the idea and hypothesis of the experiment and asked them to deliberately influence the qRNG into avoiding the negative images for the second run. 
We hypothesized that meditators could influence the outcome to less than 50% negative stimuli and explored the relationship of the effect with meditation experience and being informed about the purpose of the study.
We also added a control group consisting of participants with no meditation experience.

#### Participants

```{r}
library(tidyverse)
library(gt)

df <- study3_monks

# Data
total_participants <- nrow(df)
mean_age <- mean(df$Alter, na.rm=T)
sd_age <- sd(df$Alter, na.rm=T)
female_count <- sum(df$Geschlecht == 0, na.rm=T)
male_count <- sum(df$Geschlecht == 1, na.rm=T)

# Create the table
table_data <- data.frame(
  Characteristic = c("N", "Female", "Male", "Mean Age", "SD Age"),
  Count_Statistics = c(
    total_participants, 
    female_count, 
    male_count,
    paste0(round(mean_age, 2), " years"), 
    paste0(round(sd_age, 2), " years")
    )
)

# Print the table using kable
kable(table_data, format = "html", col.names = c("Characteristic", "Count/Statistic")) %>%
  kableExtra::kable_styling(full_width = FALSE)

```

#### Materials

We used 10 images from IAPS with very negative valence, and 10 images with neutral valence. Images were displayed on the computer screen with a size of 900x600 pixels for a duration of 300 ms. Before each image a fixation cross was shown for 2500 ms, and a black inter trial interval of 500 ms was included. The experimental program was written by one of the experimenters in C#.

#### Procedures

Participants were tested in different locations with several experimenter visiting them at convenient locations. They were tested on similar laptop devices connected to a qRNG. First, they were asked for meditation experience and state affect. After the first run of 400 trials the study was explained to them with the help of a chart. Then followed the second run, again with 400 trials. They were then asked for state affect a second time, whether they felt they succeeded in avoiding negative images and about their strategy.


::: {.callout-tip title="Data" collapse="true"}
-   [Download .csv](data/monks.csv)
-   [Download exp .csv](data/monks_exp.csv)
-   [Download con .csv](data/monks_con.csv)
:::

::: {.callout-note title="Resources" collapse="true"}
-   [Questionnaires](https://osf.io/kvjm2)
-   [Explanation Chart](https://osf.io/rjnmc)
-   [Stimuli](https://osf.io/ab29p/files/osfstorage)
:::

### Meditation


