---
title: "Meta-Analysis"
format: 
  html:
    page-layout: full
page-navigation: true
---

Last update: 14 July 2025

## Frequentist Meta-Analysis

::: panel-tabset
## Experimental Studies

In this analysis all Micro-Pk studies of the LMU Micro-Pk Lab are included that hypothesize the **presence** of an effect. In studies comparing experimental to control conditions, only the experimental conditions are included. The effect size for "Smokers 1" is inverted, since a two-tailed hypothesis was formulated and the resulting effect was negative. All other studies/conditions have directional hypotheses. Studies that expected a micro-Pk avoidance of certain stimuli (Smokers 2, Baseline Lucky) are inverted as well, since we hypothesized less target stimuli.

```{r}
st <- readRDS("data/overview2025-07-12.rds")

# Select studies / conditions
data <- subset(st, st$Experimental == TRUE)

knitr::kable(data)
```

### Forest Plot

The forest plot visually represents the effect sizes and confidence intervals for each study.

```{r}
#| warning: false
#| fig.height: 10

#Frequentist m-a with metafor 
library(metafor)

# Specify parameters of Exp Studies
yi=data$ES
vi=data$Var
studies=data$Study

# invert ES of Smokers 1, since the hypothesis was two-sided and the results showed a negative effect (smokers are avoiding smoking-related images)
yi[which(studies == "Smokers 1 Exp")] <- -yi[which(studies == "Smokers 1 Exp")]

# invert ES of studies with "less" hypothesis
yi[which(studies == "Smokers 2 Exp")] <- -yi[which(studies == "Smokers 2 Exp")]
yi[which(studies == "Smokers 3")] <- -yi[which(studies == "Smokers 3")]
yi[which(studies == "Baseline 1 Lucky")] <- -yi[which(studies == "Baseline 1 Lucky")]
yi[which(studies == "Baseline 2")] <- -yi[which(studies == "Baseline 2")]

# Recommended method = REML: Langan et al. 2018 https://onlinelibrary.wiley.com/doi/10.1002/jrsm.1316
# knha = Hartung method to control ES non-normality Rubio-Aparicio et al. 2018

res <- rma(
  yi,
  vi, 
  method="REML",
  #mods = ~ data$Labstudy,
  knha=TRUE,
  slab=paste(studies)
  )

# forest plot
forest(res, 
       xlab="ES", mlab="RE", psize=1,
       ilab = data$N, ilab.lab = "N",
       header=T, shade=T)

```

### Summary Statistics

These are the results of the meta-analysis. The model results reflect the overall estimated effect size, its confidence interval and whether it differs significantly from 0.

The Tau² represents the between-study variance, and the I² the heterogeneity. A significant test for Heterogeneity indicates a genuine variability of true effects across studies.

```{r}
summary.rma(res)
```

### Funnel Plot

```{r}
# funnel plot (publication bias)
funnel(res)
```

## Control Studies

In this analysis all Micro-Pk studies of the LMU Micro-Pk Lab are included that hypothesize the **absence** of an effect. In studies comparing experimental to control conditions, only the control conditions are included. To ensure comparability, all studies are tested with directional hypotheses in the same direction as the corresponding experimental conditions.

```{r}
# Select studies / conditions
data <- subset(st, st$Experimental == FALSE)

knitr::kable(data)
```

### Forest Plot

The forest plot visually represents the effect sizes and confidence intervals for each study.

```{r}
#| warning: false
#| fig.height: 8

#Frequentist m-a with metafor 
library(metafor)

# Specify parameters of Exp Studies
yi=data$ES
vi=data$Var
studies=data$Study

# invert ES of studies with "less" hypothesis
yi[which(studies == "Smokers 2 Con")] <- -yi[which(studies == "Smokers 2 Con")]

# Recommended method = REML: Langan et al. 2018 https://onlinelibrary.wiley.com/doi/10.1002/jrsm.1316
# knha = Hartung method to control ES non-normality Rubio-Aparicio et al. 2018

res <- rma(
  yi,
  vi, 
  method="REML",
  #mods = ~ data$Labstudy,
  knha=TRUE,
  slab=paste(studies)
  )

# forest plot
forest(res, 
       xlab="ES", mlab="RE", psize=1,
       ilab = data$N, ilab.lab = "N",
       header=T, shade=T)

```

### Summary Statistics

These are the results of the meta-analysis. The model results reflect the overall estimated effect size, its confidence interval and whether it differs significantly from 0.

The Tau² represents the between-study variance, and the I² the heterogeneity. A significant test for Heterogeneity indicates a genuine variability of true effects across studies.

```{r}
summary.rma(res)
```

### Funnel Plot

```{r}
# funnel plot (publication bias)
funnel(res)
```
:::
